
\newgeometry{left=25mm,	right=25mm, top=18mm}
\chapter*{Preface}
%\textbf{\huge{Preface}}
\vspace{-12pt}The purpose of this project is to design and implement a control system that can maintain a reaction wheel inverted pendulum in upright position using only internally mounted sensors.

This report has been written by a group of students on the sixth semester of "Electronics and IT" at Aalborg University, with specialization in Control Engineering.
The reader should have a basic knowledge on Electronic Engineering, specially in Modeling and Control Theory, and Convex Optimization, although specific topics will be described in more detail. Code for the implementation is written in \texttt{C++} and the reader is assumed to be able to comprehend this programming language. 

Special thanks to Simon Jensen (assistant engineer), Simon Vestergaard Johansen (business PhD) and Benjamin Krebs (employee of Cobham SATCOM) for their help along the project. Final thanks to the group supervisors, John-Josef Leth and Palle Andersen (associated professors of the Department of Electronic Systems at Aalborg University), for their guidance during the semester.

\textbf{Reading Instructions}\\
\vspace{-6pt}\\
\noindent The report is structured in three parts. Part I contains an analysis of the system, which includes a description of the given setup, the derivation of the dynamic model and the acquisition of the parameters of the system. Part II deals with the design and implementation of the controller and the complementary filter used to measure the angular position of the frame. Part III includes the acceptance tests made to the system and the conclusions that can be derived from the project.

The attached DVD contains a digital copy of this report, all the data and Matlab files needed to plot the figures in the report, data sheets, the code needed to run the controller, the code needed for the implementation of the optimization, the Senstools manual and three videos of the controlled system.  

\textbf{Text by:}\\
\vspace{-5pt}
\begin{table}[H]
	\centering
		\begin{tabular}{c c c}
			\underline{\phantom{JAERJAERJAERJAERGO}} & \phantom{cookies} & \underline{\phantom{JAERJAERJAERJAERGO}} \\
			Bjørn Kitz			& \phantom{cookies} & Julien Br\'ehin		\\
			&&\\
			\underline{\phantom{JAERJAERJAERJAERGO}} & \phantom{cookies} & \underline{\phantom{JAERJAERJAERJAERGO}} \\
			Mikael Sander			& \phantom{cookies} & Niels Skov Vestergaard		\\
			&&\\
	    \multicolumn{3}{c}{\underline{\phantom{JAERJAERJAERJAERGO}}}\\
	    \multicolumn{3}{c}{Noelia Villarmarzo Arruñada}\\				
		\end{tabular}
\end{table}

\pagebreak
\restoregeometry