\chapter{System Description}\label{systemDescription}
One-frame Cubli is a non-linear unstable system which is capable of laying on one of its corners as long as it is properly controlled, using the inertia created in the reaction wheel present in the setup.



This system is composed of several hardware parts, listed in the following table. \fxnote{Include picture of the real model, mark all the parts in the picture}

\begin{table}[H]
	\begin{tabular}{|l|p{6.7cm}|}
		\hline %-----------------------------------------------------------------------------------
		\textbf{No.} &\textbf{Part} 			\\
		\hline %-----------------------------------------------------------------------------------
		1            & Frame           			\\
		\hline %-----------------------------------------------------------------------------------
		2            & Reaction wheel      		\\
		\hline %-----------------------------------------------------------------------------------
		3            & BeagleBone Black (microcontroller)  \\
		\hline %-----------------------------------------------------------------------------------
		4            & Potentiometer			\\
		\hline %-----------------------------------------------------------------------------------
		5            & Inertia Measurement Units (IMU)       			\\
		\hline %-----------------------------------------------------------------------------------
		6            & Brushless DC-motor   	\\
		\hline %-----------------------------------------------------------------------------------
		7            & Motor control board     	\\
		\hline %-----------------------------------------------------------------------------------
		8            & Jump brake (servomotor)		    	\\
		\hline %-----------------------------------------------------------------------------------
		9            & Connecting and breakout board		    	\\
		\hline %-----------------------------------------------------------------------------------
	\end{tabular}0
	\caption{Main parts of the Cubli setup}
\label{TableAAUCubliComponent}
\end{table}

The BeagleBone Black, the break servomotor, the Maxon motor control board and the motor itself are mounted directly on the frame. On the motor shaft a freewheel is mounted. 

There are 2 pieces of IMU mounted on the frame to measure the acceleration and angular velocity of that frame. The latter is fixed to the platform via a potentiometer so the angular position of the frame can be measured.

To connect the BeagleBone Black to the other units like the Maxon motor control board and the IMU and potentiometer there is a connecting and breakout board.\fxnote{Shouldn't we state who has made it ? J.}

The Cubli at Aalborg University is a complete finished mechanical and electronic system and has been built by others. From the previous groups that have been working on it, some of the parameters have been found. To confirm and investigate the configuration of the mechanical parts changes has been made to the Cubli and the new parameters have not been measured and verified.

