\section{Motor}
\label{sec:Motor}


\subsection{Brushless DC-Motor}
To control the reaction wheel a brushless DC-motor is used. 
The brushless motor (EC 45 flat, 251601) can take a nominal current of 2.33 A, and 23 A at very short peaks.It has a mechanical time constant of 12,4 ms \cite{MaxonMotors}. The nominal current puts a limit on the control signal that can be sent to the motor control board.\fxnote{Should this control signal be mentioned here?}.
\fxnote{Should there be made a table listing the motors data instead of writing a paraghap with the info?}


\subsection{Motor Control Board}
Connected between the BeagleBone and the Brushless DC-motor is a ESCON Module 50/5, which is a motor control board. It is specifically made to work with ESCON motors (which the EC 45 flat is) and can be configured with a program provided by Maxon.\fxnote{provide link to maxonwebsite and the program for the configuration}

PWM frquency is \si{53,6 kHz}\fxnote{its this done correctly?}.
The Buildin 

The control board has a setup selected by the previous group working with the Cubli setup. The PWM signal has a range of 10 \% to 90 \%, and the current is limited to 4 A at 90 \% and -4 A at 10 \%. 

The internal controller of the board is running in current mode. This is a control loop that will keep the set current while the motor runs. It takes a signal, representing a current, as an input and then regulates the voltage over the motor to counteract back-EMF.

\subsection{Jump Brake}
The last important part included on the system is the braking mechanism, which is used for making the frame go from rest to vertical position. 

To perform this task the motor spins up the reaction wheel and when it has enough kinetic energy the braking mechanism suddenly brake it. This makes that all the energy of the wheel is then transfer to the frame, which reaches the vertical position.
